---
name: Veronica 
surname: Judson
position: "PhD Student"
address: "University of Wisconsin Madison"
phone: 828-508-0936
email: "vjudson@wisc.edu"
github: veronicajjudson
linkedin: Veronica Judson
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::hyndman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Professional Training

 * Wilderness First Responder Certification 
Landmark Learning, Cullowhee, NC, December 2019

 * CPR and Adult First Aid Certification 
Landmark Learning, Cullowhee, NC, December 2019

 * NEXT AVL, August 2019- May 2020 
Selected to represent UNCA as a mentee in a mentoring program with other local universities in Western North Carolina. Partnered with a professional in the Asheville area to enhance my workplace and networking skills.  


# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Master of Mathematics: Statistics", "2021", "University of North Carolina Asheville", "Asheville, North Carolina"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Nobel Prizes

```{r}
tribble(
  ~Year, ~Type, ~Desc,
  2026, "Political Science", "Awarded for her exemplory work in being a badass student"
) %>% 
  brief_entries(
    glue::glue("Nobel Prize in {Type}"),
    Year, 
    Desc
  )
```

